Online Appendix

### 2021-04-19 src/online_appendix.Rmd

- Cluster 1:

- Cluster 2:

- Cluster 3:

- Cluster 4:

- Cluster 5:

- Cluster 6:

>>>>

- Cluster 1: Medium sized mostly rural cluster; slow mean upload speeds; high workday temporal variation.

- Cluster 2: Small rural cluster; highest mean upload speeds; slowdown more in evening.

- Cluster 3: Medium sized mixed cluster; fast mean upload speeds; medium temporal variation.

- Cluster 4: Rural reference LAD; medium mean upload speeds; high temporal variation.

- Cluster 5: Small suburban cluster; fast mean upload speeds; slowdown more in evening.

- Cluster 6: Large mixed cluster; slowest aggregate mean upload speeds; low workday temporal variation.

- Cluster 7: Small suburban cluster; fast mean upload speeds; medium temporal variation.

- Cluster 8: Small mainly surburban cluster; slow mean upload speeds; high workday temporal variation.

- Cluster 9: Large, more urban cluster; fast mean upload speeds; lowest workday temporal variation.
